---
title: "A comparison between war time speech and peaceful time speech"
output:
  html_notebook: default
  html_document: default
---
```{r, message=FALSE, warning=FALSE, include=FALSE}
#Please modify the following paths:

#NECESSARY PACKAGES

#Please make sure all package referred in this file are properly loaded too
######################################################################################################################
source("D:/Columbia University/Spring2017-Applied Data Science/Project_1_Bz2290/Spr2017-Proj1-bz2290/doc/Package.R")
######################################################################################################################

#Functions needed
######################################################################################################################
source("D:/Columbia University/Spring2017-Applied Data Science/Project_1_Bz2290/Spr2017-Proj1-bz2290/lib/Functions.R")
######################################################################################################################

##PREPRCESSIONING OF THE DATA##

#Please also modify the path within Preprocess.R too
#########################################################################################################################
source("D:/Columbia University/Spring2017-Applied Data Science/Project_1_Bz2290/Spr2017-Proj1-bz2290/output/Preprocess.R")
#########################################################################################################################
```

I. INTRODUCTION

There are two groups of presidential speeches chosen, while the first group is chosen while U.S.has either directly or undirectly invovled, or there is tense moments happening in the internaitonal community. The second group of speeches are choosen during the time when the U.S. economy is booming. We hope to utilize sentiment ananlysis and other related techniques to see if there are any differences or similarities betweeen those two groups, or if there are any similiarites within each group. 

This notebook was prepared with the following environmental settings:
```{r, echo=FALSE}
print(R.version)
```


II.SENTENCE LENGTH ANALYSIS

After the data preprocessing (Please refer to "Preprocess.R" for details), we first examine the sentence length of speeches with respect to two groups. We first take a look at the general sentence length for each of the speakers:
```{r, echo=FALSE}
par(mfrow=c(1,1),mar = c(9, 5, 2, 0))
sentence=emotion.matrix[,1:4]
sentence=subset(sentence,as.character(sentence$President) %in% c(speech.selected.war,speech.selected.peace))
sentence$Pop = factor(sentence$President)
sentence$Ordered=reorder(sentence$Pop,sentence$nword,mean,order=T)
beeswarm(nword~Ordered, 
         data=sentence,
         horizontal = FALSE, 
         pch=1, col="purple",
         cex=0.5, cex.axis=0.8, cex.lab=0.8,
         spacing=5/nlevels(sentence$Ordered),
         las=2,ylab="Number of words",
         xlab="",
         main="Inauguartion speeches")
abline(h=c(1,24),col="red")
```

We see that from all speeches I have choosen, they all have a majority of their sentences within 25 words, and there are only a few president who gives extremely long sentences during his speeches.

Then we take a closer look at individual speeches, we can see that almost all president give a shorter speeches in their second terms compared to theris first ones. For example, we observed that from Lincoln's speeches:
```{r, echo=FALSE,fig.height = 5,fig.width = 10}
sentence=emotion.matrix[,1:4]
sentence=subset(sentence,as.character(sentence$President) %in% c(speech.selected.war[1],speech.selected.war[2]))
sentence$Pop = factor(sentence$President)
sentence$Ordered=reorder(sentence$Pop,sentence$nword,mean,order=T)
beeswarm(nword~Ordered, 
         data=sentence,
         horizontal = FALSE, 
         pch=1, col="purple",
         cex=0.8, cex.axis=1, cex.lab=1.2,
         spacing=5/nlevels(sentence$Ordered),
         las=2,ylab="Number of words",
         xlab="",las=1,
         main="Inauguartion speeches")
```
The number of sentences as well as the length are all significantly smaller compared to his first one.
We can also check Franklin D. Roosevelt:
```{r, echo=FALSE,fig.height = 5,fig.width = 10}
par(mfrow=c(1,2))
sentence=emotion.matrix[,1:4]
sentence=subset(sentence,as.character(sentence$President) %in% c(speech.selected.war[5],speech.selected.war[6]))
sentence$Pop = factor(sentence$President)
sentence$Ordered=reorder(sentence$Pop,sentence$nword,mean,order=T)
beeswarm(nword~Ordered, 
         data=sentence,
         horizontal = FALSE, 
         pch=1, col="purple",
         cex=0.5, cex.axis=0.9, cex.lab=1.0,
         spacing=5/nlevels(sentence$Ordered),
         las=2,ylab="Number of words",
         xlab="",las=1,
         main="Inauguartion speeches")

sentence=emotion.matrix[,1:4]
sentence=subset(sentence,as.character(sentence$President) %in% c(speech.selected.war[6],speech.selected.war[7]))
sentence$Pop = factor(sentence$President)
sentence$Ordered=reorder(sentence$Pop,sentence$nword,mean,order=T)
beeswarm(nword~Ordered, 
         data=sentence,
         horizontal = FALSE, 
         pch=1, col="purple",
         cex=0.5, cex.axis=0.9, cex.lab=1.0,
         spacing=5/nlevels(sentence$Ordered),
         las=2,ylab="Number of words",
         xlab="",las=1,
         main="Inauguartion speeches")
```
We see that from the second to the fourth speeches, both the sentences' lengths and the number of sentences have decreased from one speech to another. However, if we examine the distribution of their sentence's length distribution, we will find something interesting:
```{r, echo=FALSE}
p.1 = Quantile_plot(c(speech.selected.war[3],speech.selected.war[4]))
p.2 = Quantile_plot(c(speech.selected.war[5],speech.selected.war[6]))
p.3 = Quantile_plot(c(speech.selected.war[9],speech.selected.peace[2]))
p.4 =Quantile_plot(c(speech.selected.war[10],speech.selected.peace[4]))
multiplot(p.1, p.2, p.3, p.4, cols = 2)
```

The above graphs are plotted based on the sentences whose number of words are below 25, which is the majority sentences' length for presidential speeches I selected. We see from the above four graphs that the presidential speeches from the same speaker, surprisingly have a very similar distribution with regard to the number of words used in the sentences.

III.SENTIMENT ANALYSIS

1.Emotion Barplot analytics

After we have examined the length of sentences, we turn our attention to a more interesting asepct of text mining ananlysis - sentiment analysis. I performed the analysis by appling NRC sentimet function to sentences, and calculate a weighted score of emotion "anger", "anticipation", "disgust", "fear", "joy", "sadness", "surprise", "trust", "negative", "positive" at each sentence of each presidential speeches I selected (Please refer to "Preprocess.R" for details).

First of all, let us take a look at the emotion barplots created for presidential speeches in the "peace" group:
```{r, echo=FALSE}
par(mfrow=c(2,2))
Emotion_Barplot(speech.selected.peace[1])
Emotion_Barplot(speech.selected.peace[2])
Emotion_Barplot(speech.selected.peace[3])
Emotion_Barplot(speech.selected.peace[4])
```


There is no doubt that the top three emotions in each of these four speeches are the same, and the rank of other emotions are not very different.What worth mentioning is that "fear" always comes in fourth. Having postive emotions in the top is not out of our expectations, but we should dig a little bit deeper of the sentences that express "fear" attitudes of the speakers. We also observed another interesting pattern when we examined a partial list of barplot from the "war" group:
```{r, echo=FALSE}
par(mfrow=c(2,2))
Emotion_Barplot(speech.selected.war[1])
Emotion_Barplot(speech.selected.war[3])
Emotion_Barplot(speech.selected.war[6])
Emotion_Barplot(speech.selected.war[8])
```

Surprisingly, positive emotions still makes up the top two emotions in these speeches, and there are only one speeches whose top emotion is not positive, which is the second speech given by Lincoln, during the time when the civil war is about to end:
```{r, echo=FALSE}
par(mfrow=c(1,1))
Emotion_Barplot(speech.selected.war[2])
```

Compared to Lincoln's first speech, we see that the rank of negative emotions actually goes up even the civil war is about to end, but another president who has a similiar experience, of course, this time, the second world war, has a different change of emotions during his speech:
```{r, echo=FALSE}
par(mfrow=c(2,2))
Emotion_Barplot(speech.selected.war[5])
Emotion_Barplot(speech.selected.war[6])
Emotion_Barplot(speech.selected.war[7])
```

We see that the rank of the negative emotion "fear" is decreasing from one speech to another rather than going up.

For now, we have observed that emotion "fear" always comes fourth in our barplot of emotions for the "peace" group, the emotion of presidential speeches during war time is surprisingly positive, and two presidents whose speeches were given thorought out wars have opposite change on emotion "fear".In order to shed lights into these patterns, I decided to utilize other analysis to derive more insights.

I decided to examine the sentences that carry the emotions of interest to see if I can find more interesting things.
First, let us examine the "fear" sentences from presidents in the "peace" group:
```{r, echo=FALSE}
print(speech.selected.peace[1])
Emotion_Sentences(pop=speech.selected.peace[1])[4,]


print(speech.selected.peace[2])
Emotion_Sentences(pop=speech.selected.peace[2])[4,]


print(speech.selected.peace[3])
Emotion_Sentences(pop=speech.selected.peace[3])[4,]


print(speech.selected.peace[4])
Emotion_Sentences(pop=speech.selected.peace[4])[4,]
```
We can conclude that three of the four sentences above show that the presidents who give out these speeches is afraid of activities that are not compatible with Universal values.

Then,let us examine the "fear" sentences from Lincoln's first speech:
```{r, echo=FALSE}
Emotion_Sentences(pop=speech.selected.war[1])[4,]
```
and the "fear" sentence from the second speech:
```{r, echo=FALSE}
Emotion_Sentences(pop=speech.selected.war[2])[4,]
```
From these two sentences, we see that the "fear" sentence is the govenrment will not attack viciously on someone or some group of people, while the sentence of interest in the second speech clearly express his wish for the civil war to end. More historical analysis can possibliy dig in the experiecne he had during the war as well as his feelings towards it to better explain this change of fcous on Lincoln's fear sentences throughout the civil war.

Now let us take a look at the fear sentences from FranklinDRoosevelt's speeches:
```{r, echo=FALSE}
Emotion_Sentences(pop=speech.selected.war[5])[4,]
```

```{r, echo=FALSE}
Emotion_Sentences(pop=speech.selected.war[6])[4,]
```

```{r, echo=FALSE}
Emotion_Sentences(pop=speech.selected.war[7])[4,]
```
We see that the first two sentences are mainly focusing on taking actions to attack or counter negative situations. There are many envents happened during his two speeches, so there are many possibilities of what he is referring to. The last sentence kind of shows his optimism towards gaining victory in the war.


2.Cluster Plot analytics

The fact that the speeches from both the war and non-war groups share similar top emotions intrigues me to see whether I can perform a cluster analysis to classify these speeches into different classes based on their emotions. Cluster analysis are based on the emotion scores of each presidential speech and a k-means cluster algorithm is also deployed.

I first tried two clusters to analyze the war group:

```{r, echo=FALSE}
km.res=kmeans(presid.summary.war[,-1],2,iter.max=200,nstart=5)
fviz_cluster(km.res, 
             stand=F, repel= TRUE,
             data = presid.summary.war[,-1], xlab="", xaxt="n",
             show.clust.cent=FALSE)
```

We can generally group these speeches into two groups based on whether they are before or after the thrid speeches given by FranklinDRoosevelt. But I feel like puting the fourth speech from Roosevelet into cluster one is not appropriate, so I also performed cluster analysis using three clusters:

```{r, echo=FALSE}
km.res=kmeans(presid.summary.war[,-1],3,iter.max=200,nstart=5)
fviz_cluster(km.res, 
             stand=F, repel= TRUE,
             data = presid.summary.war[,-1], xlab="", xaxt="n",
             show.clust.cent=FALSE)


```

The second cluster plot seems to be better and we see that the general emotion from FranklinDRoosevelt speeches changes dramatically, as his three speeches belong to three different clusters seperately.

Similiary, I also performed cluster analysis on the peace group:
```{r, echo=FALSE}
km.res=kmeans(presid.summary.peace[,-1],2,iter.max=200,nstart=5)
fviz_cluster(km.res, 
             stand=F, repel= TRUE,
             data = presid.summary.peace[,-1], xlab="", xaxt="n",
             show.clust.cent=FALSE)
```

Which do not reveal many interesting results as the number of speeches selected are not big.

At last, I performed cluster analysis on all of them:
```{r, echo=FALSE}
km.res=kmeans(presid.summary.all[,-1],4,iter.max=200,nstart=5)
fviz_cluster(km.res, 
             stand=F, repel= TRUE,
             data = presid.summary.all[,-1], xlab="", xaxt="n",
             show.clust.cent=FALSE)
```

```{r, echo=FALSE}
km.res=kmeans(presid.summary.all[,-1],3,iter.max=200,nstart=5)
fviz_cluster(km.res, 
             stand=F, repel= TRUE,
             data = presid.summary.all[,-1], xlab="", xaxt="n",
             show.clust.cent=FALSE)
```

From either the analysis using three clusters or the analysis using four clusters, we can see that we are not be able to distinctly distinguish speeches from war time and non war time, as they coexist in these clusters. This does not come as a surprise since our emotion barplot shows similiar results.


IV. END

We have discussed several intersting patterns in both the "war" speech group and "peace" speech group. The patterns are certainly interesting and there are many of them deserve more digging to better expalin why these patterns exist. I hope you enjoy my blog and thank you for reading!


